Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-05 paper.qmd
Change normalisation spelling to American

The parameter vector, $\vec{\theta}$, depends on the choice of $g$, and can be considered part of 'model fitting' in the traditional sense. Common choices for $g$ include tSNE, UMAP, PHATE, TriMAP, or PaCMAP, although in theory any function that maps the entire space $\mathbb{R}^p$ to a subset of $\mathbb{R}^k$ is suitable. Any input requirements for the data (such as normalisation, or preprocessing through the use of PCA or similar) is considered part of the function $g$.

>>>>

The parameter vector, $\vec{\theta}$, depends on the choice of $g$, and can be considered part of 'model fitting' in the traditional sense. Common choices for $g$ include tSNE, UMAP, PHATE, TriMAP, or PaCMAP, although in theory any function that maps the entire space $\mathbb{R}^p$ to a subset of $\mathbb{R}^k$ is suitable. Any input requirements for the data (such as normalization, or preprocessing through the use of PCA or similar) is considered part of the function $g$.
